---
title: "autodict"
author:
  - name: "Rebecca W."
    affiliation: "The University of Kansas"
  - name: "Felix G."
    affiliation: "The University of Kansas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{autodict}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(autodict)
```

# Introduction

The purpose of the `autodict` package is to...

- Read in files (individually or in a batch)
- Gleam metadata and descriptive information about the data set
- Compile that information into a new Excel workbook to be used in generating 
pages for an in-house data dictionary

*Currently, this package is dependent on having clean and consistent data. This*
*means that cleaning the data must be done separately for these functions to*
*work as intended!*

## General Workflow

Generally, the workflow for this package is as follows:

### Read in files with `get_files_from_path()`

`get_files_from_path()` takes in a `path` (default: `"."`) to a directory that 
you want to read files from. This function parses through the directory 
recursively, reading in files as specified by the `file_types` tag (default: 
`c("csv", "xlsx")`).

Currently, this function can only read in .csv and .xlsx files.

The `keep_dir` tag is a boolean that determines whether the names of the data
frames will include the original path of the files (useful if saving as CSV - 
`keep_dir = TRUE`) or if the names should only be the source file name, without
the path (useful if saving as XLSX - `keep_dir = FALSE` - also the default val).

`get_files_from_path()` returns a combined list of data frames. Each data frame
is a file that was read in.

For example, the following code block will search through everything within
`Data/All Data`. It will parse through files within `All Data` as well as any
additional folders nested within.

```{r}
df_list <- get_files_from_path(path = "Data/All Data", file_types = c("csv", "xlsx"), keep_dir = TRUE)
df_list
names(df_list)
```

If all of this data is clean and represented as you expect it should, you can 
go ahead and run `save_data_dictionary()`, as described in the next section.

### Write dictionary file with `save_data_dicitonary()`

`save_data_dictionary` takes in the complete list of data frames as `data` and
the desired save path and directory as `source_path` (default = "data"). This
function appends "_dictionary.xlsx" to `source_path` to denote that the saved
file represents a data dictionary, specifically.

Then, the function creates a workbook with the `openxl` package. It parses
through each data and creates a unique worksheet for each, appending it to the
workbook. After each data is represented as a unique worksheet, it will export
the workbook as `Dictionaries/source_path_dictionary.xlsx`, creating the
"Dictionaries" folder if one does not already exist. This folder will be created
**in the directory that your working file is saved.**

The functions saves this output and returns the file path that it was saved at.

For example, the following code will save the dictionary of `df_list`, which we
generated in the last step.

```{r}
save_dict_csv(data = df_list)
```

### XLSX vs CSV considerations

In this workflow, saving an XLSX and a CSV have different needs. Ultimately, the
output from `get_files_from_path` function can be used for both `save_dict_csv`
and `save_dict_xlsx` without issue. However, you should pay attention to the
`keep_dir` tag that you use.

If you use `get_files_from_path(..., keep_dir = TRUE)`...

- **Saving a CSV file** will save each data frame recursively in a file folder
structure identical to that which it had originally (within the "Dictionaries"
folder, of course).
- **Saving an XLSX file** will behave incorrectly, as the name of each worksheet
that composes the workbook will be filled with the file path, instead of a
descriptive name generated from the file name.

- When in doubt...
  - **Saving a CSV: ** use `keep_dir = TRUE`
  - **Saving an XLSX: ** use `keep_dir = FALSE`
