---
title: "autodict"
author:
  - name: "Rebecca W."
    affiliation: "The University of Kansas"
  - name: "Felix G."
    affiliation: "The University of Kansas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{autodict}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(autodict)
```

# Introduction

The purpose of the `autodict` package is to...

- Read in files (individually or in a batch)
- Gleam metadata and descriptive information about the data set
- Compile that information into a new Excel workbook to be used in generating 
pages for an in-house data dictionary

*Currently, this package is dependent on having clean and consistent data.*



## General Workflow

Generally, the workflow for this package is as follows:

### Read in files with `get_files_from_path()`

`get_files_from_path()` takes in a `path` (default: `"."`) to a directory that 
you want to read files from. This function parses through the directory 
recursively, reading in files as specified by the `file_types` tag (default: 
`c("csv", "xlsx")`).

Currently, this function can only read in .csv and .xlsx files.

`get_files_from_path()` returns a combined list of data frames. Each data frame
is a file that was read in.

For example, the following code block will search through everything within
`Data/All Data`. It will parse through files within `All Data` as well as any
additional folders nested within.

```{r}
df_list <- get_files_from_path(path = "Data/All Data", file_types = c("csv", "xlsx"))
```

If all of this data is clean and represented as you expect it should, you can 
go ahead and run `save_data_dictionary()`, as described in the next section.

### Save Data Dictionary


